Evaluating the leaf photosynthetic rates?

### 2016-07-14 Main.Rmd
書き進め。

---
title: "Evaluating the leaf photosynthetic rates?"
author: "KeachMurakami"
date: "June 24, 2016"
bibliography: ~/Dropbox/R/List.bib
csl: new-phytologist.csl
output:
  html_document:
    toc: true
    # toc_float: true
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: true
    pandoc_args: [
    "--latexmathml"
    ]
  # word_document:
  #   toc: true
  #   fig_caption: true
  #   pandoc_args: [
  #   "--latexmathml"
  #   ]
---

@@

```{r Spectra}
HID_raw <-
  fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)

HIDs <-
  HID_raw %>%
  setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
  select(1, HPS = 12, MH = 21)

@@

SPDs <-
  left_join(HIDs, Sun, by = "wavelength") %>%
    SPDnorm(from = 350, to = 750, integratedPFD = 100) %>%
    select(-Absorptance) %>%
    SPD + theme_bw2() +
    xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))

@@

  geom_rect()

  annotate()

```

@@

  Several studies have reported that the SPD of the ML affected the *P*~n~ of leaves [e.g. @McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
  To eliminate this direct effect, the photosynthetic parameters usually measured under identical SPD conditions in the agricultural and horticultural researches.
  The most prevailing light source might be blue and red LED light sources.

@@

```{r FigOutput, fig.cap = CapSPD}
SPDs
```

# References

>>>>

---
title: "Evaluating the leaf photosynthetic rates?"
author: "KeachMurakami"
date: "June 24, 2016"
bibliography: ~/Dropbox/R/List.bib
# csl: new-phytologist.csl
output:
    html_document:
    toc: true
    # toc_float: true
    depth: 3
    theme: sandstone
    self_contained: TRUE
    fig_caption: true
    pandoc_args: [
      "--latexmathml"
    ]
# word_document:
#   toc: true
#   fig_caption: true
#   pandoc_args: [
#   "--latexmathml"
#   ]
---

@@

```{r Spectra}

# set integrate ranges
PFD_integrate_min <- 350
PFD_integrate_max <- 750

HID_raw <-
  fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)

HIDs <-
  HID_raw %>%
  setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
  select(1, HPS_ = 12, MH_ = 21)

HPS_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_HPS.txt", skip = 50, nrow = 2000) %>%
  rename(wavelength = V1, value = V2)

HPS_Ocean_PFD <-
  smooth.spline(HPS_Ocean_raw$wavelength, HPS_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

HPS_Ocean <-
  HPS_Ocean_raw %>%
  mutate(value = value * 100 / HPS_Ocean_PFD, variable = "HPS")

MH_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_MH.txt", skip = 50, nrow = 2000) %>%
  rename(wavelength = V1, value = V2)

MH_Ocean_PFD <-
  smooth.spline(MH_Ocean_raw$wavelength, MH_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

MH_Ocean <-
  MH_Ocean_raw %>%
  mutate(value = value * 100 / MH_Ocean_PFD, variable = "MH")

@@

SPDs <-
  # left_join(HIDs, Sun, by = "wavelength") %>%
  Sun %>%
  SPDnorm(from = 350, to = 750, integratedPFD = 100) %>%
  select(-Absorptance) %>%
  gather(variable, value, -wavelength) %>%
  bind_rows(., HPS_Ocean) %>%
  bind_rows(., MH_Ocean) %>%
  filter(between(wavelength, 350, 800)) %>%
  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
  theme_bw2(legend = "right") +
  geom_line() +
  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))

@@

CapInteract <-
  "Fig. 2 Spectral photon flux density distribution of light . The distributions at a PFD of 100 µmol m<sup>--2</sup> s<sup>--1</sup> within 400--750 nm are shown."
```

@@

  A number of studies have reported that the SPD of the ML affected the *P*~n~ of leaves [e.g. @McCree1972AM; @Inada1976PCP; @Hogewoning_et_al2012PC].
  To eliminate this direct effect, the photosynthetic parameters usually measured under identical SPD conditions in the agricultural and horticultural researches.
  The most prevailing light source might be blue and red LED light sources.

@@

```{r FigSPD, fig.cap = CapSPD}
SPDs
```

```{r FigInteract, fig.cap = CapInteract}
InteractionView
```
# References
